---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# :package: `bnfimage` – API client to BnF images

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html#maturing)
[![R-CMD-check](https://github.com/Rekyt/bnfimage/workflows/R-CMD-check/badge.svg)](https://github.com/Rekyt/bnfimage/actions)
[![codecov](https://codecov.io/gh/Rekyt/bnfimage/branch/master/graph/badge.svg)](https://codecov.io/gh/Rekyt/bnfimage)
[![CRAN-version](https://www.r-pkg.org/badges/version/bnfimage)](https://cran.r-project.org/package=bnfimage)
<!-- badges: end -->

`bnfimage` is an R client for the [BnF images API](http://api.bnf.fr/api-iiif-de-recuperation-des-images-de-gallica).
The Bibliothèque Nationale de France (BnF), has a online repository called [Gallica](https://gallica.bnf.fr/) containing millions of scanned documents. The BnF offers an API to access all the images programmatically, `bnfimage` lets you access it through R.

The BnF Image API is implemented following the [International Image Interoperability Framework](https://iiif.io/) (IIIF) with Image API implemented using v.1.1, the Presentation API implemented using v.2.0, and the Search API not yet implemented.

## :wrench: Installation

You can install the development version of bnfimage with:

``` r
remotes::install_github("Rekyt/bnfimage")
```

## :memo: Example

You can extract images with the `bi_image()` function:

```{r example}
library(bnfimage)
eiffel_tower = bi_image(
  identifier = "ark:/12148/btv1b9055204k/f1",
  region     = "full",
  size       = c(1500, 750),
  rotation   = 0,
  quality    = "native",
  format     = "png")

str(eiffel_tower)

eiffel_tower
```

You can get the metadata associated with this image using `bi_metadata()`:

```{r metadata_example}
eiffel_metadata = bi_metadata("ark:/12148/btv1b9055204k/f1")

str(eiffel_metadata, max.l = 2)
```

You can query both data and associated metadata using the `bi_all_data()` function and get a nicely formatted tibble:

```{r all_data_1}
bi_all_data("ark:/12148/btv1b9055204k/f1", size = c(15, 7))
```

You can also provide several identifiers to `bi_all_data()`:

```{r all_data_2}
bi_all_data(c("ark:/12148/btv1b9055204k/f1",
              "ark:/12148/btv1b90055455/f1"))
```

## :boom: Rate limitation

```{r rate-limitation-chunk, child = "man/rmdchunks/_fundiversity_functions.Rmd"}
```

## :page_facing_up: Data license

Note that the images from Gallica have [a specific license](https://gallica.bnf.fr/edit/und/conditions-dutilisation-des-contenus-de-gallica) so make sure to check the license of the images you plan to reuse.
As a general rule, non-commercial reuse is free of charge but the source should be speficied as "Source gallica.bnf.fr / Bibliothèque nationale de France" or "Source gallica.bnf.fr / BnF". Commercial reuse should be license specifically following the [price list](https://www.bnf.fr/fr/faire-une-utilisation-commerciale-dune-reproduction).


## :information_source: Related projects

[`gargallica`](GuillaumePressiat/gargallica) is a collection of script and functions to retrieve data from the regular Gallica API.

## :speech_balloon: Code of Conduct

Please note that the `bnfimage` project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
