---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `bnfimage` – API client to BnF images

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![Travis build status](https://travis-ci.org/Rekyt/bnfimage.svg?branch=master)](https://travis-ci.org/Rekyt/bnfimage) [![codecov](https://codecov.io/gh/Rekyt/bnfimage/branch/master/graph/badge.svg)](https://codecov.io/gh/Rekyt/bnfimage) [![CRAN-version]( https://www.r-pkg.org/badges/version/bnfimage)](https://cran.r-project.org/package=bnfimage)

`bnfimage` is an R client for the [BnF images API](http://api.bnf.fr/api-iiif-de-recuperation-des-images-de-gallica).
The Bibliothèque Nationale de France (BnF), has a online repository called [Gallica](https://gallica.bnf.fr/) contaning millions of documents that are scanned. The BnF now offers an API to access all the images programmatically, and this package allows you to access it through R.

The BnF Image API is implemented following the [International Image Interoperability Framework](https://iiif.io/) (IIIF) with Image API implemented using v.1.1, the Presentation API implemented using v.2.0, and the Search API not yet implemented.

## Installation

You can install the development version of bnfimage with:

``` r
remotes::install_github("Rekyt/bnfimage")
```

## Example

You can extract images with the `bi_image()` function:

```{r example}
library(bnfimage)
eiffel_tower = bi_image(
  identifier = "ark:/12148/btv1b9055204k/f1",
  region     = "full",
  size       = c(1500, 750),
  rotation   = 0,
  quality    = "native",
  format     = "png")

str(eiffel_tower)

eiffel_tower
```

You can get the metadata associated with this image using `bi_metadata()`:

```{r metadata_example}
eiffel_metadata = bi_metadata("ark:/12148/btv1b9055204k/f1")

str(eiffel_metadata, max.l = 2)
```

You can query both data and associated metadata using the `bi_all_data()` function and get a nicely formatted tibble:

```{r all_data_1}
bi_all_data("ark:/12148/btv1b9055204k/f1", size = c(15, 7))
```

You can also provide several identifiers to `bi_all_data()`:

```{r all_data_2}
bi_all_data(c("ark:/12148/btv1b9055204k/f1",
              "ark:/12148/btv1b90055455/f1"))
```

## Related projects

[`gargallica`](GuillaumePressiat/gargallica) is a collection of script and functions to retrieve data from the regular Gallica API.

## Code of Conduct

Please note that the `bnfimage` project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
