---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `bnfimage` – API client to BnF images

<!-- badges: start -->
<!-- badges: end -->

`bnfimage` is an R client for the [BnF images API](http://api.bnf.fr/api-iiif-de-recuperation-des-images-de-gallica)

## Installation

You can install the development version of bnfimage with:

``` r
remotes::install_github("Rekyt/bnfimage")
```

## Example

You can extract images with the `bi_image()` function:

```{r example}
library(bnfimage)
eiffel_tower = bi_image(
  identifier = "ark:/12148/btv1b9055204k/f1",
  region     = "full",
  size       = c(1500, 750),
  rotation   = 0,
  quality    = "native",
  format     = "png")

str(eiffel_tower)

image(eiffel_tower)
```

You can get the metadata associated with this image using `bi_metadata()`:

```{r metadata_example}
eiffel_metadata = bi_metadata("ark:/12148/btv1b9055204k/f1")

str(eiffel_metadata)
```

## Code of Conduct

Please note that the `bnfimage` project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
