---
title: "bnfimage - Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bnfimage - Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!--
# Pre-render with
knitr::knit("vignettes/_bnfimage.Rmd", output = "vignettes/bnfimage.Rmd")
-->

```{r vignette-setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "./"
)
```

```{r setup}
library(bnfimage)
```

The BnF Gallica image library contains thousands of freely accessible images of historical interests. It provides an Application Programming Interface to access it ([see their documentation](https://api.bnf.fr/api-iiif-de-recuperation-des-images-de-gallica#scroll-nav__1)). The access is possible through the [IIIF](https://iiif.io/) API. The goal of `bnfimage` is to let you access this API directly from R.

## Accessing Images - `bi_image()`

To get a specific image, you first need to get its identifier from Gallica.
The identifier is a string that begins with `ark:/`. It is accessible from browsing [Gallica](https://gallica.bnf.fr) as the URL of the object such as: `https://gallica.bnf.fr/ark:/12148/bpt6k10411495/f11.item#` giving the id `ark:/12148/bpt6k10411495/f11`.

### Single Image

To download a single image you can use the `bi_image()` with the identifier of the object:

```{r bi-image}
bi_image("ark:/12148/bpt6k10411495/f11")
```


#### Image Crop

This displays a small portion of the image as by default this functions only returns the top left corner of the image from 0 to 500px in both directions.

To get the full image you can use the argument `region` with the value `"full"`:

```{r bi-image-region-full}
bi_image("ark:/12148/bpt6k10411495/f11", region = "full", size = c(150, 150))
```

Otherwise if you want to crop a specific region in the image you can define it as length 4 numeric vector specifiying the coordinates of the top left most point and the bottom right point. For example if you want to extract the image from 1250px x and 1300px y to 1600px x and 1650px y you would call:

```{r bi-image-region-crop}
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(160, 165))
```


#### Image size

As you noticed previous commands specified a `size` argument.
It corresponds to the size of the extracted image. It can be equal to `"full"` so
that the extracted region is returned without being scaled.


```{r bi-image-size-full}
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = "full")
```

It can also be a numeric vector of lenth 2 that gives the size at which the extracted region should be scaled:


```{r bi-image-size-small}
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(25, 70))
```

Other options exist in the [IIIF Image API](https://iiif.io/api/image/1.1/#4-2-size) but are not yet implemented in `bnfimage`.


#### Rotation

`bnfimage` supports a `rotation` argument that returns a rotated image. By default the returned image is not rotated (`rotation = 0`). The argument is the clockwise rotation angle in degrees. When the rotation angle is not a multiple of 90° then the background color used is white.


```{r bi-image-region-crop-rotation}
# No rotation
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(80, 82),
         rotation = 0)

# 90° clockwise rotation
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(80, 82),
         rotation = 90)

# Non-multiple of 90° rotation
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(80, 82),
         rotation = 153)
```


#### Color

To lower bandwidth it is possible to directly ask for transformed bit-depth of the returned image through the `quality` argument.
It can take four values:

1. `"native"` which returns the image as stored in the BnF database,
1. `"color"` with the image in full color using 24 bits per pixel,
1. `"grey"` with the image in greyscale using 8 bits per pixel,
1. `"bitonal"` where is pixel is either black or white using 1 bit per pixel.



```{r bi-image-quality}
# Native
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(160, 165),
         quality = "native")

# Color
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(160, 165),
         quality = "color")

# Grey
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(160, 165),
         quality = "gray")

# Bitonal
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650),
         size = c(160, 165),
         quality = "bitonal")
```


#### Format

The images can be returned as different files format. This can be changed through the `format` argument which can take all these values:

* `"jpg"` JPEG format (which is used by default),
* `"gif"` GIF format,
* `"png"` PNG,
* `"jp2"` JP2,
* `"pdf"` PDF,
* `"tif"` TIFF.

```{r bi-image-format}
# JPG image
bi_image("ark:/12148/bpt6k10411495/f11", region = "full", size = c(75, 75),
         format = "jpg")

# PDF image
bi_image("ark:/12148/bpt6k10411495/f11", region = "full", size = c(75, 75),
         format = "pdf")
```


#### Saving the image

To save the images you can use the function `image_write()` in the `magick`
package. `image_write()` can accept any image filetype:

```{r bi-image-save}
img = bi_image("ark:/12148/bpt6k10411495/f11", size = c(160, 165),
               region = c(1250, 1300, 1600, 1650))

magick::image_write(img, "./my_image.png")
```

The second argument specifies the file path. Refer to the help of the function
through `?magick::image_write` to get an overview of all the arguments and uses.


### Multiple Images

To access several images you can use a list of identifier and wrap calls
to `bi_image()` using `lapply()`:

```{r bi-several-imgs}
several_ids = c("ark:/12148/bpt6k10411495/f11", "ark:/12148/bpt6k10411495/f13",
                "ark:/12148/bpt6k10411495/f15")

several_imgs = lapply(several_ids, bi_image, region = "full",
                      size = c(200, 200))

several_imgs
```

## Accessing Metadata - `bi_metadata()`

One interest of the BnF image library is the richness of the metadata associated
with an image. For the moment bnfimage only converts metadata to a giant list
to make it accessible.

### Single Image

Using a single image identifier you can retrieve the metadata of an image
through the function `bi_metadata()`. The first argument is the identifier of
the image as for `bi_image()`:

```{r bi-metadata}
met = bi_metadata("ark:/12148/bpt6k10411495/f11")

str(met, max.level = 1)
```

The metadata contains much information on the actual image as well as its
context.

### Multiple Images

Similarly as for `bi_image()` to access the metadata of several images you can
wrap the calls to `bi_metadata()` through a list of identifiers using
`lapply()`:

```{r bi-metadata-all}
several_met = lapply(several_ids, bi_metadata)

str(several_met, max.level = 2)
```


## Accessing Both Images and Metadata - `bi_all_data()`

The `bi_all_data()` function can be used to quickly retrieve both the images as
well as the associated metadata of one or several images. The outputs stores the
identifier of an image in a column, the actual image in a second one, and the
associated metadata in a third one:

```{r bi-all-data}
bi_all_data(c("ark:/12148/bpt6k10411495/f11", "ark:/12148/bpt6k10411495/f12"),
            size = c(200, 200))
```


## Rate Limitation

```{r child="../man/rmdchunks/_rate_limitation.Rmd"}
```
