---
title: "bnfimage - Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bnfimage - Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bnfimage)
```

<!-- Should use vcr cassette to record all interactions in vignette -->

The BnF Gallica image library contains thousands of freely accessible images of historical interests. It provides an Application Programming Interface to access it ([see their documentation](https://api.bnf.fr/api-iiif-de-recuperation-des-images-de-gallica#scroll-nav__1)). The access is possible through the [IIIF](https://iiif.io/) API. The goal of `bnfimage` is to let you access this API directly from R.

## Accessing Images

To get a specific image, you first need to get its identifier from Gallica.
The identifier is a string that begins with `ark:/`. It is accessible from browsing [Gallica](https://gallica.bnf.fr) as the URL of the object such as: `https://gallica.bnf.fr/ark:/12148/bpt6k10411495/f11.item#` giving the id `ark:/12148/bpt6k10411495/f11`.

### Single Image - `bi_image()`

To download a single image you can use the `bi_image()` with the identifier of the object:

```{r bi-image}
bi_image("ark:/12148/bpt6k10411495/f11")
```

This displays a small portion of the image as by default this functions only returns the top left corner of the image from 0 to 500px in both directions.

To get the full image you can use the argument `region` with the value `"full"`:

```{r bi-image-region-full}
bi_image("ark:/12148/bpt6k10411495/f11", region = "full")
```

Otherwise if you wan to crop a specific region in the image you can define it as length 4 numeric vector specifiying the coordinates of the top left most point and the bottom right point. For example if you want to extract the image from 1250px x and 1300px y to 1600px x and 1650px y you would call:

```{r bi-image-region-crop}
bi_image("ark:/12148/bpt6k10411495/f11", region = c(1250, 1300, 1600, 1650))
```

Saving the images. How to save them and which format?

### Multiple Images

Similar way for multiple images.

## Accessing Metadata

One interest of the BnF image library is the amount of metadata associated with
metadata.
For the moment bnfimage only converts metadata to a giant list so need more
transformation to be usable.

### Single Image

Same as before, images are identified through their identifier. For composed documents blabla.

### Multiple Images

Idem

## Accessing Both Images and Metadata

Short condensed format to extract all corresponding data for all images.
