---
title: "bnfimage - Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bnfimage - Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bnfimage)
```

<!-- Should use vcr cassette to record all interactions in vignette -->

General explanation on BnF image library. Can Access thousands of images.
Centralized protocol and framework (IIIF).

## Accessing Images

To get a specific image, first need to find identifier

### Where to find identifier on Gallica?

identifier is a string that begins with `ark:/`

### Single Image

For example for an image with `ark:/XXXABCid` identifier can get image using
`bi_image("ark:/XXXABCid")` and retrieve

Detail parameters. To crop specific images.

Saving the images. How to save them and which format?

### Multiple Images

Similar way for multiple images.

## Accessing Metadata

One interest of the BnF image library is the amount of metadata associated with
metadata.
For the moment bnfimage only converts metadata to a giant list so need more
transformation to be usable.

### Single Image

Same as before, images are identified through their identifier. For composed documents blabla.

### Multiple Images

Idem

## Accessing Both Images and Metadata

Short condensed format to extract all corresponding data for all images.
